Describing the C-Space of Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-07-29 dit-paper_ieee.tex
our work updated

  \subsection{Our work}
    In this paper, we extend the work of \cite{george2009characterization} to the
    asynchronous case. In section \ref{sct:asyncDIT}, we present an extension of
    the concept of DIT adapted to the asynchronous case called first periodic DIT
    ($t_d$), along with an algorithm to determine its existence and value for any system. In Section
    \ref{sct:asyncCspace}, we show how to describe the C-space of an asynchronous
    system based on the DBF test, and we show why the interval $[t_d, t_d + H]$ is
    sufficient to consider. In section ???, we present a simulation where we find that........

>>>>

  \subsection{Our work}
    In this paper, we extend the work of \cite{george2009characterization} to the
    asynchronous case. In section \ref{sct:asyncDIT}, we present an extension of
    the concept of DIT adapted to the asynchronous case called first periodic DIT
    ($t_d$) along with an algorithm to determine its existence and value for any system,
    then we show the influence of some factors on its existence. In Section
    \ref{sct:asyncCspace}, we show how to describe the C-space of an asynchronous
    system based on the DBF test, we show why the interval $[t_d, t_d + H]$ is
    sometimes sufficient to consider and we give a numerical example.
    Finally, in section ???, we present a simulation where we find that........
